Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-11-19 src/tex/ms.tex
Update figures

% What's new?
In this paper, we used a birefringence model with higher order terms which include the frequency dependence of amplitude birefringence to perform a more accurate parameter estimation (PE).
We also performed Bayesian inference on events in GWTC-3, the third GW transient catalog.
We included 70 binary black hole merger events with smallest false alarm rate $\leq1\mathrm{yr^{-1}}$, which are listed in \citet{GWTC_3_population}.\footnote{GW190720 is included in list, however, we could not successfully perform PE with it. Details on GW190720 will be mention in Discussion.}

@@

\begin{figure}[h]
    \script{kappa_stacked.py}
    % \includegraphics[width=\columnwidth]{figures/kappa_stacked.pdf}
    \caption{
        The posterior of $kappa$ for all 70 events included in this study.
        Each color represent a different event.
        These posterior are used to calculate the constraint on $\kappa$ in the following.
    }
    \label{fig:kappa_stacked}
\end{figure}

@@

\begin{figure}[h]
    \script{corner_Gaussian.py}
    % \includegraphics[width=\columnwidth]{figures/corner_Gaussian.pdf}
    \caption{
        The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
    }
    \label{fig:corner_Gaussian}
\end{figure}

@@

\begin{figure}[h]
    \script{violin_kappa.py}
    % \includegraphics[width=\columnwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $kappa$ for all 70 events included in this study.
        Each violin represents a different event.
        The violins are sorted by the quotient of median and standard deviation of the posterior.
    }
    \label{fig:violin_kappa}
\end{figure}

@@

\begin{figure}[h]
    \script{corner_GW190521.py}
    % \includegraphics[width=\columnwidth]{figures/corner_GW190521.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW190521.
        The colors in the plot are the PE with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3} and the PE done by us with the frequency dependent birefringence.
        The plot shows that frequency dependent birefringence cannot break the degeneracy between $\kappa$ and $\iota$.
    }
    \label{fig:corner_GW190521}
\end{figure}

>>>>

% What's new?
In this paper, we used a birefringence model with higher order terms which include the frequency dependence of amplitude birefringence to perform a more accurate parameter estimation (PE).
We also performed Bayesian inference on events in GWTC-3, the third GW transient catalog.
We included 70 binary black hole merger events with smallest false alarm rate $\leq1\mathrm{yr^{-1}}$, which are listed in \citet{GWTC_3_population}.\footnote{GW190720 is included in the list in \citet{GWTC_3_population}, however, we could not successfully perform PE with it. Details on GW190720 will be mention in Discussion.}

@@

\begin{figure}[h]
    \script{kappa_stacked.py}
    \includegraphics[width=\columnwidth]{figures/kappa_stacked.pdf}
    \caption{
        The posterior of $\kappa$ for all 70 events included in this study.
        Each color represent a different event.
        These posterior are used to calculate the constraint on $\kappa$ in the following.
    }
    \label{fig:kappa_stacked}
\end{figure}

@@

\begin{figure}[h]
    \script{corner_Gaussian.py}
    \includegraphics[width=\columnwidth]{figures/corner_Gaussian.pdf}
    \caption{
        The posterior of $\mu$ and $\sigma$ of the population distribution of $\kappa$.
    }
    \label{fig:corner_Gaussian}
\end{figure}

@@

\begin{figure*}[ht]
    \script{violin_kappa.py}
    \includegraphics[width=\textwidth]{figures/violin_kappa.pdf}
    \caption{
        The violin plot shows the posterior of $\kappa$ for all 70 events included in this study.
        Each violin represents a different event.
        The violins are sorted by the quotient of median and standard deviation of the posterior.
    }
    \label{fig:violin_kappa}
\end{figure*}

@@

\begin{figure}[h]
    \script{corner_GW190521.py}
    \includegraphics[width=\columnwidth]{figures/corner_GW190521.pdf}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW190521.
        The colors in the plot are the PE with GR done by LVK without cosmological reweighing \citep{GWTC-2.1, GWTC-3} and the PE done by us with the frequency dependent birefringence.
        The plot shows that frequency dependent birefringence cannot break the degeneracy between $\kappa$ and $\iota$.
    }
    \label{fig:corner_GW190521}
\end{figure}
